Apache Flink\texttrademark: Stream and Batch Processing in a Single Engine

### 2016-05-25 paper.tex
add acknowledgements

\begin{abstract}
Apache Flink is an open-source system for processing streaming and batch data. Flink is built on the philosophy that many classes of data processing applications, including real-time analytics, continuous data pipelines, historic data processing (batch), and iterative algorithms (machine learning, graph analysis) can be expressed and executed as pipelined fault-tolerant dataflows. In this paper, we present Flink's architecture and expand on how a (seemingly diverse) set of use cases can be unified under the same execution model.
\end{abstract}

@@

>>>>

\begin{abstract}
Apache Flink \footnote{The authors of this paper make no claim in being the sole inventors or implementers of the ideas behind Apache Flink that are presented, but rather a group of people that attempt to accurately document these concepts and their significance in writing. For a complete list see \autoref{sec:acknowledgements}} is an open-source system for processing streaming and batch data. Flink is built on the philosophy that many classes of data processing applications, including real-time analytics, continuous data pipelines, historic data processing (batch), and iterative algorithms (machine learning, graph analysis) can be expressed and executed as pipelined fault-tolerant dataflows. In this paper, we present Flink's architecture and expand on how a (seemingly diverse) set of use cases can be unified under the same execution model.
\end{abstract}

@@

\vspace{-4mm}
\section{Acknowledgements}
\vspace{-2mm}
\label{sec:acknowledgements}
The development of the Apache Flink project is overseen by a self-selected team of active contributors to the project. A Project Management Committee (PMC) guides the project's ongoing operations, including community development and product releases. At the current time of writing this, the list of Flink committers (excluding any affiliated authors) are : M\'arton Balassi, Ufuk Celebi, Gyula F\'ora, Alan Gates, Fabian Hueske, Vasia Kalavri, Aljoscha Krettek, Andra Lungu, Robert Metzger, Maximilian Michels, Chiwan Park, Till Rohrmann, Henry Saputra, Matthias J. Sax, Sebastian Schelter, Timo Walther, Daniel Warneke, ChengXiang Li, and Greg Hogan. In addition to these individuals, we want to acknowledge the broader Flink community of more than 180 contributors.
